---
title: "Computational Reproducibility"
subtitle: "Dynamic Reporting"
date: last-modified # display the date of the last edit
author: 
  - name: "Adrian Büchli"
    orcid: 1234-1234-1234-12345
    affiliation: "University of Bern"
    email: adrian.buechli@unibe.ch
format:
  html:
    toc: true # add a table of contents
---

# Exemplary Data Analysis

Within this file, we will *analyse* some data to show how quarto works.

```{r}
library("dplyr") # data wrangling
library("ggplot2") # plotting
library("kableExtra") # tables
```


## Creating a Table

We have read in the data and will now create a table to display relevant information.

```{r}
summaries <- read.csv("/home/rstudio/project/contents/module_3_workflow_management/demo/snakemake/work/2_yearly_winners.csv")

summaries |>
  kable(caption = "Most common names of newborns in the city of Zurich by year and sex")
```

We can additionally plot the data in a nice little graphic.

```{r}
datclean <- read.csv("/home/rstudio/project/contents/module_3_workflow_management/demo/snakemake/work/1_names_clean")

datclean |>
  # The upper bound is deliberate: the data set gains a year of records over
  # time, and bounding the window keeps this figure matching its caption.
  filter(year >= 2021, year <= 2025) |>
  group_by(sex, name) |>
  summarise(births = sum(births)) |>
  slice_max(order_by = births, n = 10) |>
  ggplot(aes(x = reorder(name, births), y = births)) +
  facet_wrap(~ sex, scales = "free") +
  geom_bar(stat = "identity") +
  labs(x = "Name", y = "Births", 
       title = "") +
  coord_flip() +
  theme_minimal()
```

We can also plot my own name over time.

```{r}
datclean <- read.csv("/home/rstudio/project/contents/module_3_workflow_management/demo/snakemake/work/3_selected_names.csv")

datclean |>
  group_by(sex, name, year) |>
  filter(name %in% c("Christian", "Adrian")) |>
  ggplot(aes(x = year, y = births, color = name)) +
  geom_line() +
  geom_point() +
  scale_color_viridis_d() +
  labs(x = "Year", y = "Births", color = "") +
  expand_limits(y = 0) +
  theme_minimal()
```

In 1998, the most common male name was `r filter(summaries, year == 1998, sex == "male")$name` whereas the most common female name was `r filter(summaries, year == 1998, sex == "female")$name`.

